A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2019-08-01 paper/data/plotsWithTikz.tex
finished rome and north figures, only grid remaining

\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}
\subfloat[\label{fig:cr-res-2}{Aspect ratio vs no.~of vertices}]{
\centering
%===================================
% Crossing Resolution Aspect Ratio
%===================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,ylabel style={yshift=-0.2cm},legend style={at={(0.425,1.35)}, anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mycoloredlist, mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100},ylabel={Aspect Ratio}, xlabel={Number of Vertices}, ytick={1,2.5,10,25,100,250,1000,2500,10000}, xmin=10, xmax=100,ymode=log, log ticks with fixed point,tick pos=left, ymajorgrids,]

@@

\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}
\subfloat[\label{fig:cr-res-4}{No.~of iterations vs no.~of vertices}]{
\centering
%==================================
% Crossing Resolution Iterations
%==================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,ylabel style={yshift=-0.2cm},legend style={at={(0.425,1.35)}, anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mycoloredlist,  ylabel={Iterations}, xlabel={Number of Vertices}, mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100}, xmin=10,
xmax=100, ytick={0,2000,4000,...,14000},tick pos=left, ymajorgrids]

>>>>

\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}
\subfloat[\label{fig:cr-res-2}{Aspect ratio vs no.~of vertices}]{
\centering
%===================================
% Crossing Resolution Aspect Ratio
%===================================
\begin{tikzpicture}
\begin{axis}[axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,ylabel style={yshift=-0.2cm},legend style={at={(0.425,1.35)}, anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mycoloredlist, mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100},ylabel={Aspect Ratio}, xlabel={Number of Vertices}, ytick={1,3,10,30,100,300,1000,3000,10000}, xmin=10, xmax=100,ymode=log, log ticks with fixed point,tick pos=left, ymajorgrids,]

@@

\legend{{Unrestricted},{AR-restricted~~},{Huang et al.},{Argyriou et al.}}
\end{axis}
\end{tikzpicture}}
\subfloat[\label{fig:cr-res-4}{No.~of iterations vs no.~of vertices}]{
\centering
%==================================
% Crossing Resolution Iterations
%==================================
\begin{tikzpicture}
\begin{axis}[scaled y ticks = false,axis x line*=bottom,xlabel style={yshift=0.2cm},axis y line*=left,ylabel style={yshift=-0.2cm},legend style={at={(0.425,1.35)}, anchor=north,legend columns=2,draw=none}, width=0.475\textwidth,cycle list name=mycoloredlist,  ylabel={Iterations}, xlabel={Number of Vertices}, mark repeat={5},xtick={10,20,30,40,50,60,70,80,90,100}, xmin=10,
xmax=100, ytick={0,2000,4000,...,14000},tick pos=left, ymajorgrids]
